Argennon: A Scalable Smart Contract Platform

### 2022-04-03 tex/A.tex
Update Chapter 1
This is the first draft.

Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Restructure the paper
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\begin{document}
    %\maketitle
    \tableofcontents

@@

    \chapter{The Argon Language}\label{ch:argon-lang}
    \input{sections/argon}

@@

    \chapter{Networking Layer}\label{ch:networking}
    \section{Normal Mode}\label{sec:normal-mode}
    Unlike conventional blockchains, Argennon does not use a P2P network architecture. Instead, it uses a
    client-server topology, based on a permission-less list of ZK-EDB servers. ZK-EDB servers are a
    crucial part of the Argennon ecosystem, and they form the backbone of the Argennon networking layer.
    \note{not yet written...}

@@

    \chapter{The Argennon Blockchain}\label{ch:argennon-blockchain}
    \input{sections/elements}

@@

@@

    \section{Concurrent Transaction Validation}\label{sec:concurrency}
    \input{sections/concurrency}

    \chapter{Governance}\label{ch:governance}
    \section{ADAGs}\label{sec:adags}
    The Argennon Decentralized Autonomous Governance system (ADAGs)
    \note{not yet written...}
\end{document}

>>>>

\begin{document}
    \maketitle
    \begin{abstract}
        Argennon is a cloud based blockchain and smart
        contract platform which tries to solve shortcomings of existing platforms. The Argennon blockchain uses a hybrid
        proof of stake (POS) consensus protocol, which is based on participation of every Argennon user.

        Thanks to the
        cloud based design of the Argennon blockchain, transaction validation does not require costly computational
        resources, and normal personal computers with limited hardware capabilities can actively participate in the
        Argennon consensus protocol. This property makes Argennon a truly decentralized and democratic blockchain and
        one of the most secure existing platforms.

        By using cryptographic accumulators, the integrity of data on the Argennon cloud is guaranteed, and there
        is no need for trusting cloud servers. At the same time, by using a smart clustering algorithm the network usage
        and the overhead of the commitment scheme is kept manageable.
    \end{abstract}
    \tableofcontents

@@

@@

    \chapter{Networking Layer}\label{ch:networking}

    \section{Normal Mode}\label{sec:normal-mode}
    Unlike conventional blockchains, Argennon does not use a P2P network architecture. Instead, it uses a
    client-server topology, based on a permission-less list of ZK-EDB servers. ZK-EDB servers are a
    crucial part of the Argennon ecosystem, and they form the backbone of the Argennon networking layer.
    \note{not yet written...}

@@

    \chapter{The Argennon Blockchain}\label{ch:argennon-blockchain}

@@

    \input{sections/elements}

@@

    \chapter{Governance}\label{ch:governance}

    \section{ADAGs}\label{sec:adags}
    The Argennon Decentralized Autonomous Governance system (ADAGs)
    \note{not yet written...}

    \chapter{The Argon Language}\label{ch:argon-lang}
    \input{sections/argon}
\end{document}

### 2022-04-03 tex/sections/avm.tex
Restructure the paper
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data structures for executing requests are constructed. This step is
designed in a way that can be done fully in parallel for each request without any risks of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution dag} and in
the final step, request are executed using this data structure.

@@

The Argennon Smart Contract Execution Environment can be seen as a machine for executing Argennon applications to
fulfill HTTP requests, produce their HTTP responses and update related heap chunks. The AscEE executes requests
sequentially \footnote{Actually requests are executed in parallel but by performing data dependency analysis the
result is guaranteed to be identical
with sequential execution of requests.} and each request has a separate \emph{execution session}. Execution sessions
are separate sessions of executing smart contract's code in order to fulfill \emph{external} HTTP requests. An
external request is a request that is not made by another Argennon application.

@@

The persistent data of an Argennon application is stored in heap chunks. An application may have several heap chunks
with different sizes, and can remove or
resize its chunks or allocate new chunks. Every chunk belongs to exactly one application. Only the owner application can
modify a chunk but there is no restrictions for reading a chunk \footnote{The reason behind this type of access
control design is the fact that smart contract
code is usually immutable. That means if a smart contract does not implement a
getter mechanism for some parts of its internal data, this functionality can never
be added later, and despite the internal data is publicly available, there will be no
way for other smart contracts to use this data on-chain.}.

When an application allocates a new heap chunk, the identifier of the new chunk is not generated by
the AscEE. Instead, the application can choose an identifier itself, provided it has a correct format. This
is an important feature of the AscEE heap, which allows applications to use the AscEE heap as a dictionary
data structure \footnote{also called a map.}.
Since the \texttt{chunkID} is a prefix code, any application has its own identifier space, and an application
can easily find unique identifiers for its chunks.

@@

Chunks and access blocks have different purposes. Chunks are intended for simplifying proof checking of the data
stored in the Argennon cloud \footnote{Note that
the Argennon cloud uses cryptographic accumulators for preserving data integrity.} and access blocks are
required for better parallelization of the request execution. An application should put the data it predicts is
needed for validating a block in the same chunk and the data it predicts is needed in a single execution
session in the same access block.

>>>>

The AscEE executes the requests contained in each block of the Argennon
blockchain in a three-step procedure. The first step is the \emph{preprocessing step}. In this step, the required
data structures for executing requests are constructed. This step is
designed in a way that can be done fully in parallel for each request without any risks of data races. The second
step is the \emph{Data Dependency Analysis (DDA) step}.
In this step by analyzing data dependency between requests, the AscEE determines requests that can be run in parallel
and requests that need to be run sequentially. This information is represented using an \emph{execution dag} and in
the final step, requests are executed using this data structure.

@@

The Argennon Smart Contract Execution Environment can be seen as a machine for executing Argennon applications to
fulfill HTTP requests, produce their HTTP responses and update related heap chunks. The AscEE executes requests
sequentially\footnote{Actually requests are executed in parallel but by performing data dependency analysis the
result is guaranteed to be identical
with sequential execution of requests.} and each request has a separate \emph{execution session}. Execution sessions
are separate sessions of executing smart contract's code in order to fulfill \emph{external} HTTP requests. An
external request is a request that is not made by another Argennon application.

@@

The persistent data of an Argennon application is stored in heap chunks. An application may have several heap chunks
with different sizes, and can remove or
resize its chunks or allocate new chunks. Every chunk belongs to exactly one application. Only the owner application can
modify a chunk but there is no restrictions for reading a chunk\footnote{The reason behind this type of access
control design is the fact that smart contract
code is usually immutable. That means if a smart contract does not implement a
getter mechanism for some parts of its internal data, this functionality can never
be added later, and despite the internal data is publicly available, there will be no
way for other smart contracts to use this data on-chain.}.

When an application allocates a new heap chunk, the identifier of the new chunk is not generated by
the AscEE. Instead, the application can choose an identifier itself, provided it has a correct format. This
is an important feature of the AscEE heap, which allows applications to use the AscEE heap as a dictionary
data structure\footnote{also called a map.}.
Since the \texttt{chunkID} is a prefix code, any application has its own identifier space, and an application
can easily find unique identifiers for its chunks.

@@

Chunks and access blocks have different purposes. Chunks are intended for simplifying proof checking of the data
stored in the Argennon cloud\footnote{Note that
the Argennon cloud uses cryptographic accumulators for preserving data integrity.} and access blocks are
required for better parallelization of the request execution. An application should put the data it predicts is
needed for validating a block in the same chunk and the data it predicts is needed in a single execution
session in the same access block.

### 2022-04-03 tex/sections/elements.tex
Restructure the paper
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

An application identifier, \texttt{applicationID}, is
a unique prefix code generated by the \emph{applications} prefix tree. (See Section~\ref{sec:identifiers}.)
An application identifier can be considered as the address of an application and has the following standard symbolic
representation:
\begin{verbatim}
<application-id> ::= <decimal-prefix-code>
<decimal-prefix-code> ::= <dec-num>"."<decimal-prefix-code> | <dec-num>
\end{verbatim}
where \texttt{<dec-num>} is a normal decimal number between $0$ and $255$.

For example \texttt{21.255.37}, \texttt{0}, \texttt{11.6} and \texttt{2.0.0.0.0}, are valid application addresses.

@@

@@

\section{Transactions}\label{sec:transactions}
\emph{subsection is outdated and needs updating!}

Every Argennon transaction consists of two \texttt{i\_invoke\_dispatcher} instructions, the first instruction always
transfers the proposed fee of the transaction in ARGs from a sender account to the fee sink accounts, and
the second performs the requested operation. If the first instruction fails, the transaction will not be added to
the Argennon blockchain.

Users interact with AVM smart contracts using
the second \texttt{i\_invoke\_dispatcher} instruction of a transaction.
Transferring all assets, including ARG, is done by that instruction.

The \texttt{i\_invoke\_dispatcher} instruction invokes the \texttt{dispatcher} method of a smart contract. Every AVM
smart contract has a \texttt{dispatcher} method, and the Argennon protocol requires
the \texttt{dispatcher} method to accept an HTTP request as its argument and
return an HTTP response.

As a result, every Argennon transaction contains two HTTP requests. Besides these HTTP requests, the
transaction is also required to contain a resource declaration object, specifying the maximum amount of resources
it needs for execution.

\note{Argennon smart contracts use HTTP as the application protocol and they are advised to have a RESTful API design.}

\subsection{Resource Declaration}\label{subsec:resource-declaration}
\emph{subsection is outdated and needs updating!}

Every Argennon transaction is required to specify a cap for all the resources it needs. This
includes memory, network and processor related resources. If during emulation, a transaction reaches one of its
pre-declared resource caps, executing any AVM instruction which uses that resource, will result in an AVM exception.

As we know, every Argennon transaction consists of two \texttt{i\_invoke\_dipatcher} instructions. The first
instruction is always considered as a \emph{free} instruction and resources spent during its execution
session will not be counted. Therefore, only the second instruction could fail due to exceeding resource limits.

The Argennon protocol defines an execution cost for
every AVM instruction, reflecting the amount of resources its emulation needs. Every
transaction is required to specify two maximum execution costs: \texttt{maxInternalCost}
and \texttt{maxExternalCost}. The \emph{external} execution cost of a transaction is the \textbf{overall} cost of its
\texttt{invoke\_dispatcher} and \texttt{invoke\_later} instructions,\footnote{By overall cost, we mean the execution
cost needed for reaching the next instruction.}. The remaining execution cost will be considered as
the \emph{internal} cost. If a transaction reaches one of its maximum execution costs, executing any instruction
which has that type of cost, will throw an AVM exception.

>>>>

An application identifier, \texttt{applicationID}, is
a unique prefix code generated by the \emph{applications} prefix tree. (See Section~\ref{sec:identifiers}.)
An application identifier can be considered as the address of an application and has the following standard symbolic
representation:
\begin{verbatim}
<application-id> ::= <decimal-prefix-code>
<decimal-prefix-code> ::= <dec-num>"."<decimal-prefix-code> | <dec-num>
\end{verbatim}
where \texttt{<dec-num>} is a normal decimal number between $0$ and $255$. For example \texttt{21.255.37},
\texttt{0}, \texttt{11.6} and \texttt{2.0.0.0.0}, are valid application addresses.

@@

Argennon application use HTTP as the application protocol and they are advised to have a RESTful API design.

@@

\section{Transactions}\label{sec:transactions}

An Argennon transaction consist of an HTTP request made by a user, to an Argennon application and a resource
declaration object. Transactions can only be
issued by users and applications can not create transactions. An Argennon transaction is also called
an \emph{external request}.

\subsection{Resource Declaration}\label{subsec:resource-declaration}

Every Argennon transaction needs to specify a maximum for
The Argennon protocol requires every  an execution cost for
every AVM instruction, reflecting the amount of resources its emulation needs. Every
transaction is required to specify two maximum execution costs: \texttt{maxInternalCost}
and \texttt{maxExternalCost}. The \emph{external} execution cost of a transaction is the \textbf{overall} cost of its
\texttt{invoke\_dispatcher} and \texttt{invoke\_later} instructions,\footnote{By overall cost, we mean the execution
cost needed for reaching the next instruction.}. The remaining execution cost will be considered as
the \emph{internal} cost. If a transaction reaches one of its maximum execution costs, executing any instruction
which has that type of cost, will throw an AVM exception.
